\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Benjamin Magid} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(781) 786-1881 \\ Lexington, MA} 
\address{\href{mailto:bmm2179@columbia.edu}{bmm2179@columbia.edu} \\ \href{https://bennymagid.github.io/index.html}{bennymagid.github.io} }  %

\begin{document}
	
	%----------------------------------------------------------------------------------------
	%	OBJECTIVE
	%----------------------------------------------------------------------------------------
	
	%\begin{rSection}{OBJECTIVE}
	%	
	%	{Software Engineer with 2+ years of experience in XXX, seeking %full-time XXX roles.}
	%	
	%	
	%\end{rSection}
	
	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	
	\begin{rSection}{Education}
		
		{\bf BA in Computer Science}, Columbia University \hfill {Expected 2023}\\
		\emph {Fall 2019 Dean's List Award Recipient. GPA 4.0} \\
		Relevant Coursework: Advanced Programming (C, C++), Data Structures and Algorithms (Java), Computer Science I (Java), Discrete Mathematics, Statistics I.
		
		{\bf High School Diploma} (dual enrollment at Boston University), Boston University Academy \hfill {2015 - 2019}\\
		\emph{Graduated Summa Cum Laude. GPA 3.79. SAT 1580. }
		
		
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	% TECHINICAL STRENGTHS	
	%----------------------------------------------------------------------------------------
	\begin{rSection}{SKILLS}
		
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			Technical Skills & Java, Python, C, Excel VBA, Git, Javascript, Dash App Design, ARIMA Modeling.
			\\
			Soft Skills & Coordination, Project Management, Analysis, Organization, Curiosity.\\
		\end{tabular}\\
	\end{rSection}
	
	\begin{rSection}{EXPERIENCE}
		
		\textbf{Data Analyst and Research Intern} \hfill May 2020 - September 2020\\
		The Beacon Hill Institute for Public Policy Research \hfill \textit{Remote Position}
		\begin{itemize}
			\itemsep -3pt {} 
			\item Developed and designed a novel, Python-based comparative analytics Dash App for U.S. state competitiveness data based on proprietary BHI index models. Edited with Jupyter Notebook and deployed with Git and Heroku. 
			\item Built ARIMA models with Python using Massachusetts tax data to predict state tax revenue during and after the COVID-19 pandemic.
			\item Implemented various Excel Macros to allow for manipulation and distribution of curated U.S. state competitiveness data.
		\end{itemize}
		
		\textbf{Creative Marketing Director} \hfill September 2020 - Present\\
		\textbf{Podcast Research Intern} \hfill May 2020 - September 2020\\
		Cress Health \hfill \textit{Remote Position}
		\begin{itemize}
			\itemsep -3pt {} 
			\item Successfully coordinated and maintained social media marketing campaigns on Instagram and Tiktok for a new-to-market, consumer-facing mental health platform, Callie. 
			\item Identified relevant and exciting episode ideas for the Cress Health podcast and spearheaded research.
		\end{itemize}
	
		\textbf{Tutor} \hfill September 2019 - Present\\
		The Tutoring and Learning Center at Columbia University \hfill \textit{New York, NY / Remote Position}
		\begin{itemize}
			\itemsep -3pt {} 
			\item Mentored a small, dynamic group of local high school sophomores in regular meetings to develop effective study habits and foster a sense of community within the nearby public-school system.  
			\item Studied pedagogy and communication techniques at weekly training sessions.
		\end{itemize}
	
		%\textbf{Digital Marketing Manager} \hfill August 2017 - August %2019\\
		%\textbf{Head Counselor, Guitar Instructor} \hfill July 2012 - %August 2017\\
		%Keys for Kids Music School \hfill \textit{Lexington, MA}
		%\begin{itemize}
		%	\itemsep -3pt {} 
		%	\item Mentored a small, dynamic group of local high school %sophomores in regular meetings to develop effective study habits %and foster a sense of community within the nearby public-school %system.  
		%	\item Studied pedagogy and communication techniques at weekly %training sessions.
		%\end{itemize}
		
	\end{rSection} 
	
	%----------------------------------------------------------------------------------------
	%	WORK EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	
	%\begin{rSection}{PROJECTS}
	%	\vspace{-1.25em}
	%	\item \textbf{Short Project Title.} {Build a project that does %something and had quantified success using A, B, and C.}
	%	\item \textbf{Short Project Title.} {Build a project that does %something and had quantified success using A, B, and C. This project's %description spans two lines and also won an award.}
	%	\item \textbf{Short Project Title.} {Build a project that does %something and had quantified success using A, B, and C. This project's %description spans two lines and also won an award.}
	%\end{rSection} 
	
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Extra-Curricular Activities} 
		\begin{itemize}
			\itemsep -3pt {} 
			\item Jazz Pianist in the Columbia University Jazz Performance Program Big Band (2019-Present)
			\item	Jazz Administrator at 89.9 WKCR FM, Columbia’s student-led, educational radio station (2019-2020)
		\end{itemize}
		
		
	\end{rSection}
	
	
	
\end{document}
